Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2013-10-11 omrp.tex
Rewrite computational results section
1. Include discussion of why the test problems were selected
2. Fix typo from inclusion of DB1

We empirically tested the effectiveness of OMRP on four problems.
The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, the third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables, and the final is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
Descriptions of CEP1, 10D, and DB1 can be found in \cite{higle1996}, \cite{kleywegt2002sample}, and \cite{donohue1995upper}, respectively.
The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.  
The problems CEP1, DB1 and newsvendor can be written as two-stage stochastic linear programs with recourse.
CEP1 and DB1 were solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}. 
The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
In all cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.

@@

\begin{figure}[htb!]
	\centering
	\subfloat[][CEP1]{
	   \label{fig:cep1_varvar}
	   \includegraphics[width=.32\textwidth]{images/cep1_varvar}}
	\subfloat[][10D]{
	   \label{fig:10d_varvar}
	   \includegraphics[width=.32\textwidth]{images/10D_varvar}}
	\subfloat[][DB1]{
	   \label{fig:db1_varvar}
	   \includegraphics[width=.32\textwidth]{images/db1_varvar}}
		\caption{
		Variance Reduction for
		(a) CEP1 and 
		(b) 10D
		(c) DB1
		for various values of $\gamma / m$.
		}
\label{fig:varvar}
\end{figure}

>>>>

We empirically tested the effectiveness of OMRP on four problems.
The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$.
The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations.
The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.
The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
Descriptions of CEP1, 10D, and DB1 can be found in \cite{higle1996}, \cite{kleywegt2002sample}, and \cite{donohue1995upper}, respectively.
The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.  
The problems CEP1, DB1 and newsvendor can be written as two-stage stochastic linear programs with recourse.
CEP1 and DB1 were solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}. 
The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
In all cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.

We made several considerations in selecting the test problems.
Newsvendor can be solved very quickly, which allows for solving a large number of independent runs for examining the small sample behavior of OMRP.
CEP1 is also easy to solve, and obtains the optimal solution $\xs$ with high probability even for small sample sizes.
This feature shows the behavior $VG$ when the gap size is determined mostly by sampling error, rather than bias.
10D demonstrates the behavior of OMRP when $|X|$ is finite.
Furthermore, 10D has a high condition number \cite{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP with the bias of the gap is significant.
The optimal solutions of both 10D and CEP1 are known, allowing for explicitly checking the computational results.
In contrast, DB1 is a large scale example, with an unknown optimal solution.
This final problems allows us to show that OMRP works on more computationally difficult problems.

@@

\begin{figure}[htb!]
	\centering
	\subfloat[][CEP1]{
	   \label{fig:cep1_varvar}
	   \includegraphics[width=.32\textwidth]{images/cep1_varvar}}
	\subfloat[][10D]{
	   \label{fig:10d_varvar}
	   \includegraphics[width=.32\textwidth]{images/10D_varvar}}
	\subfloat[][DB1]{
	   \label{fig:db1_varvar}
	   \includegraphics[width=.32\textwidth]{images/db1_varvar}}
		\caption{
		Variance Reduction for
		(a) CEP1,
		(b) 10D, and
		(c) DB1
		for various values of $\gamma / m$.
		}
\label{fig:varvar}
\end{figure}
